降低汽油精制过程中的辛烷值损失模型

### 2020-09-21 paper/B20100130029.tex
addd

\newpage
\begin{thebibliography}{99}  
\bibitem{ref1}Pedregosa, F. and Varoquaux, G. and Gramfort, A. and Michel, V.
         and Thirion, B. and Grisel, O. and Blondel, M. and Prettenhofer, P.
         and Weiss, R. and Dubourg, V. and Vanderplas, J. and Passos, A. and
         Cournapeau, D. and Brucher, M. and Perrot, M. and Duchesnay, E., Scikit-learn: Machine Learning in {P}ython, America: Journal of Machine Learning Research, 2825--2830：2011。

% \bibitem{ref2}Arandjelović R, Zisserman A, Three things everyone should know to improve object retrieval, Computer Vision and Pattern Recognition (CVPR), 2012 IEEE Conference on, IEEE, 2012: 2911-2918.  
% \bibitem{ref3}Lowe D G. Distinctive image features from scale-invariant keypoints, International journal of computer vision, 2004, 60(2): 91-110.  
 \bibitem{ref4}Hua Zhu ,[算法]图解A\* 搜索算法, https:\/\/blog.csdn.net\/JasonZhu\_csdn\/article\/details\/86266228，2020年9月21日。

>>>>

\newpage
\begin{thebibliography}{99}  
\bibitem{ref1}Pedregosa, F. and Varoquaux, G. and Gramfort, A. and Michel, V.
         and Thirion, B. and Grisel, O. and Blondel, M. and Prettenhofer, P.
         and Weiss, R. and Dubourg, V. and Vanderplas, J. and Passos, A. and
         Cournapeau, D. and Brucher, M. and Perrot, M. and Duchesnay, E., Scikit-learn: Machine Learning in {P}ython, America: Journal of Machine Learning Research, 2825--2830，2011。
 \bibitem{ref2}周志华，机器学习，北京： 清华大学出版社，23--51，2016。  
 \bibitem{ref2}李航，统计学习，北京： 清华大学出版社，47--53，2012。 
% \bibitem{ref3}Lowe D G. Distinctive image features from scale-invariant keypoints, International journal of computer vision, 2004, 60(2): 91-110.  
 \bibitem{ref4}Hua Zhu，[算法]图解A* 搜索算法，https://blog.csdn.net/JasonZhu\_csdn/article/details/8626622，2020年9月21日。
